% https://www.acm.org/binaries/content/assets/publications/consolidated-tex-template/acmart.pdf
%\documentclass[sigchi, timestamp, manuscript, screen]{acmart}
\documentclass[sigconf, screen]{acmart}

%%%%
% What packages do people load by default in LaTeX?
% https://tex.stackexchange.com/questions/553/what-packages-do-people-load-by-default-in-latex
%%%%
\usepackage{cleveref}
\usepackage{subcaption}

%%%%
% CUSTOMISE ACMART DESIGN
% https://tex.stackexchange.com/a/346309
%%%%
\setcopyright{none}
\settopmatter{printacmref=false}
\renewcommand\footnotetextcopyrightpermission[1]{}
% \pagestyle{plain}

\acmConference[ACEAI]{Affective Computing / Empathic Artificial Intelligence}{2019-2020}{Munich, Germany}

\begin{document}

\title[BodyPose - Break Slouching Habits of the Digital Age]{BodyPose - Break Slouching Habits of the Digital Age:\\Design and Evaluation of a Posture Monitoring Concept}

% AUTHOR
\author{Andreas Ellwanger}
\orcid{0000-0003-2024-9439}
\affiliation{%
  \institution{LMU Munich}
  \city{Munich}
  \state{Bavaria}
  \country{Germany}
}
\email{andreas.ellwanger@campus.lmu.de}
% AUTHOR
\author{Timo Erdelt}
\affiliation{%
  \institution{LMU Munich}
  \city{Munich}
  \state{Bavaria}
  \country{Germany}}
\email{timo.erdelt@campus.lmu.de}
% AUTHOR
\author{Samantha Kühn}
\affiliation{%
  \institution{LMU Munich}
  \city{Munich}
  \state{Bavaria}
  \country{Germany}}
\email{s.kuehn@campus.lmu.de}
% AUTHOR
\author{Johannes Tochtermann}
\affiliation{%
  \institution{LMU Munich}
  \city{Munich}
  \state{Bavaria}
  \country{Germany}}
\email{johannes.tochtermann@campus.lmu.de}

%%%%
% ABSTRACT
%%%%
\begin{abstract}
Neck, shoulder and low back pain top the list of reported work-related disorders. Frequent computer usage seems to be one decisive factor for these disorders and can thus lead to a reduced quality of life for employees.
In order to help employees prevent back pain, it is crucial to instrumentalise motivational prevention tools and education.
One approach to lower the risk for back pain is to increase healthy postural habits.
However, as employees focus on their current work, slouching habits may arise unintentionally.

We developed BodyPose as a reactive but accessible web application to detect slouching in computer-related work activities. It evaluates the upper body posture using computer vision and a rule-based system without the need for additional hardware beyond a standard webcam. With the focus on usability, it grants instant feedback using notifications. 

To evaluate the impact of BodyPose, we conducted a user study (N=3). Overall, the users reported they felt motivated to correct a bad posture and maintain healthy body alignment, both short- and long-term.
The findings imply that BodyPose may encourage users to work on their body posture and counteract potential destructive slouching habits.
\end{abstract}

%%%%
% KEYWORDS
%%%%
\keywords{Affective computing, office workspace, body posture, computer vision, PoseNet, neural network, web app, user interface, persuasive technologies.}

%%%%
% MAKE TITLE !!! DON'T MOVE
%%%%
\maketitle

%%%%
% IMPORT
%%%%
\input{content.tex}

%%%%
% BIBLIOGRAPHY
%%%%
\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography}

\end{document}
